Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2025-01-11 paper/paper.tex
minor

% TODO: add to abstract

@@

% TODO: reverse order

For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset. For example, they would add some edges based on some sophisticated heuristics tailored to that particular dataset. In addition, they manually added the clique (sex,city,income) for the prediction target of income. We do not consider these additional ___ for the generality of our approach. Meanwhile, his other apporach where the auditor does not access the real dataset does not fit our framework.

@@

% TODO: avg of 100 runs

The AI models and both the original dataset and synthetic datasets are then fed to the fairness checker. Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}. Then, applicable fairness measures are computed using the checker for both the original and the synthetic.

@@

% TODO: clarify "by common sense"

In addition, further experiments showed that, in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.

>>>>

@@

For the competition, \cite{mckenna2021winning} further manually added certain cliques based on their investigation of the competition dataset. For example, they would add some edges based on some sophisticated heuristics tailored to that particular dataset. In addition, they manually added some particular cliques like (sex,city,income) for the prediction target of income. We do not consider these additional optimizations for the generality of our approach. Meanwhile, their other apporach where the auditor does not access the real dataset does not fit our framework.

@@

The AI models and both the original dataset and synthetic datasets are then fed to the fairness checker. The synthetic datasets were generated 100 times and the fairness scores averaged across the 100 runs. Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}. Then, applicable fairness measures are computed using the checker for both the original and the synthetic.

@@

In addition, further experiments showed that, by common sense or in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.
